Measuring contrast processing in the visual system using SSVEP

### 2024-06-13 review.qmd
Make figs in place

---
title: "Measuring contrast processing in the visual system using SSVEP"
author:
  - name: Alex R. Wade
  - name: Daniel H. Baker
format: 
  #pdf:
  #  keep-tex: true
  docx:
    keep-tex: true
bibliography: WadeBaker_Review.bib
csl: visual-neuroscience.csl
execute:
  echo: false
  output: false
  include: false
---

>>>>

---
title: "Measuring contrast processing in the visual system using SSVEP"
author:
  - name: Alex R. Wade
  - name: Daniel H. Baker
format:
  docx: 
    omitFigures: true
  pdf:

    keep-tex: true

bibliography: WadeBaker_Review.bib
csl: visual-neuroscience.csl
execute:
  echo: false
  output: false
  include: false
---
